A systematic search for transiting planets in the \KT\ data

### 2015-04-22 ms.tex
nothing

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
primarily due to three major factors.  First, the superior precision
of the \kepler\ photometry enables detection of secondary stellar
eclipses, odd-even transit depth variations, and ellipsoidal
variations \citep{Batalha:2010} to a much lower level than
ground-based surveys. Second, the relatively small pixels and stable
pointing of the \kepler\ telescope has enabled the identification of
many spatially distinct blended eclipsing binaries by means of
detailed pixel-level analysis \citep{Bryson:2013} to identify shifts
in the center of light during transits.  And finally, \kepler\ is
sensitive to much smaller planets than ground-based surveys, and small
planets are much more common than the Jupiter-sized planets able to be
detected from the ground.  We note that while \citet{Santerne:2012} reported
a $\sim$35\% observational false positive rate, that study was exclusively 
focused on short-period, large candidates, among which false positives
are expected to be more likely.  \citet{Desert:2015} has observationally confirmed 
a low false positive rate for the majority of \kepler\ candidate parameter
space.

>>>>

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
primarily due to three major factors.  First, the superior precision
of the \kepler\ photometry enables detection of secondary stellar
eclipses, odd-even transit depth variations, and ellipsoidal
variations \citep{Batalha:2010} to a much lower level than
ground-based surveys. Second, the relatively small pixels and stable
pointing of the \kepler\ telescope has enabled the identification of
many spatially distinct blended eclipsing binaries by means of
detailed pixel-level analysis \citep{Bryson:2013} to identify shifts
in the center of light during transits.  And finally, \kepler\ is
sensitive to much smaller planets than ground-based surveys, and small
planets are much more common than the Jupiter-sized planets able to be
detected from the ground.
\response{We note that while \citet{Santerne:2012} reported a $\sim$35\%
observational false positive rate, that study was exclusively focused on
short-period, large candidates, among which false positives are expected to be
more likely.
\citet{Desert:2015} has observationally confirmed a low false positive rate
for the majority of \kepler\ candidate parameter space.}
